---
title: "dhyey"
author: "dm"
date: "11/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The given increasing trends of anxiety and depression, we questioned if this is due to COVID-19 getting worse. But, wait! We can see that the cases and deaths due to COVID-19 increased in general as we progress along the weeks 1 to 39. If we look closely, then we can see that the number of new cases/deaths per week actually decreases. This means that the COVID-19 is technically not getting worse! We can see this by the decreasing slope of the graph of total cases v/s weeks OR by the graph of decreasing number of cases/deaths per week v/s week as shown below. 
```{r}
timeline_graph <- read_csv("timeline_graph.csv") %>%
  filter(response == "Covid Deaths", state == "National")

ggplot(data = timeline_graph,
           mapping = aes(x = week,
                         y = percentage)) +
      geom_line(aes(x = week,
                    y = percentage)) +
      geom_point(aes(x = week,
                     y = percentage)) +
  geom_smooth(method = "lm", se = TRUE, color = "red") +
  
      theme(plot.title = element_text(size=15), 
            plot.subtitle = element_text(size=10),
            axis.text = element_text(size=10),
            axis.title = element_text(size=10),
            legend.text = element_text(size=10),
            legend.title = element_text(size=10),
            legend.key.size = unit(1, 'cm')) +
      scale_colour_manual(values = c("Covid Deaths" = "red")) +
      labs(title = "The Covid Deaths",
           subtitle = "During the Covid-19 Period",
           y = "Percentage of Deaths in the given week over the total",
           x = "Week")
```