---
title: "kayla"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(csv)
library(ggplot2)
require(mosaic)
library(mdsr)
```


```{r precovid-graph}
# create dataset from CDC
precovid_anxiety <- data.frame(Symptoms = c("No", "Yes"),
                                Percentage = c(84.4, 15.6))

# create bar chart
precovid_barchart <- ggplot(precovid_anxiety,
                            aes(x = Symptoms, y = Percentage, fill = Symptoms)) + 
  geom_col() + 
  geom_text(aes(label = Percentage), vjust=0) +
  scale_fill_manual("Symptoms",
                    values = c("No" = "plum",
                               "Yes" = "pink")) + 
#"Severe" = "palegreen"
#"Moderate" = "paleturquoise1",
  labs(title = "The Percentage of People Who Experienced Symptoms of Anxiety",
       subtitle = "In 2019 (Pre-Covid)",
       x = "Experienced Symptoms",
       y = "Percentage")

precovid_barchart

# create dataset with calculated mean percentage
covid_anxiety <- data.frame(Symptoms = c("No", "Yes"),
                            Percentage = c(82, 18))

covid_barchart <- ggplot(covid_anxiety,
                         aes(x = Symptoms, y = Percentage, fill = Symptoms)) +
  geom_col() +
  geom_text(aes(label = Percentage), vjust=0) +
  scale_fill_manual("Symptoms",
                    values = c("No" = "palegreen",
                               "Yes" = "paleturquoise1")) + 
  labs(title = "The Percentage of People Who Experienced Symptoms of Anxiety",
       subtitle = "During Covid-19",
       x = "Experienced Symptoms",
       y = "Percentage")
covid_barchart

```

> How was mental health pre-covid?
* During 2019, 9.5% of adults experienced mild, 3.4% experienced moderate, and 2.7% experienced severe symptoms of anxiety 
* 84.4% of adults aged 18 and over experienced no or minimal symptoms of anxiety 


```{r covid-graph, ggplot}
# import data
mental_health <- read_csv("mental_health.csv") %>%
  filter(State == "National")

# plot anxiety graph with ggplot
anxiety_graph <- ggplot(data = mental_health,
           mapping = aes(x = WEEK,
                         y = anxiety_percentage)) +
      geom_line(aes(x = WEEK,
                    y = anxiety_percentage),
                color = "magenta") +
      geom_point(aes(x = WEEK,
                     y = anxiety_percentage),
                 color = "magenta") + 
  geom_smooth(method='lm', formula = y~x) + 
  geom_hline(yintercept = 32.6, linetype = "dashed") +
  labs(title = "The Percentage of People Who Experienced Symptoms of Anxiety",
       subtitle = "During Covid (Weeks 1- 39)",
       x = "Week",
       y = "Percentage")

df1 <- data.frame(x1 = 5, x2 = 2.3, y1 = 30, y2 = 32.5)
df2 <- data.frame(x1 = 21.5, x2 = 18, y1 = 25.5, y2 = 23.7)

anxiety_graph + 
  annotate("text", x = 5.3, y = 29.2, label = "Week 2", colour = "red") + 
  geom_curve(
    aes(x = x1, y = y1, xend = x2, yend = y2),
    inherit.aes = FALSE,
    data = df1,
    arrow = arrow(length = unit(0.03, "npc"))) + 
  annotate("text", x = 9.4, y = 10.3, label = "Week 3", colour = "red") +
  geom_segment(aes(x = 7.3, y = 10.2, xend = 3.5, yend = 10.2),
               arrow = arrow(length = unit(0.3, "cm"))) + 
  annotate("text", x = 24, y = 25.5, label = "Week 18", colour = "red") + 
  geom_curve(
    aes(x = x1, y = y1, xend = x2, yend = y2),
    inherit.aes = FALSE,
    data = df2,
    arrow = arrow(length = unit(0.03, "npc")))

# using mosaic to find statistics and conditions
cor(mental_health$anxiety_percentage, mental_health$WEEK)
mean(mental_health$anxiety_percentage)

gm1 <- lm(anxiety_percentage ~ WEEK, data = mental_health)

msummary(gm1)

mplot(gm1, which = 1)
mplot(gm1, which = 2)
```
> How has mental looked during Covid-19? 
* The general trend of percentage of people who experienced symptoms of anxiety during the 39 weeks of covid is generally positive 
* The average percent of people who experienced symptoms of anxiety during Covid is 18%
* The correlation coefficient (r) between anxiety percentage and week on the national level is 0.44
* There is a weak, positive association between week and anxiety iwith a coefficient of determination (R^2) of 19.6% 
* This linear model has a residual standard error of 3.765
* Residual standard error is the standard deviation of the residuals, so smaller residual standard errors means predictions are better
* In this case, the number is high so this means the predictions are not good
* There seems to be a huge deviation from the line of best fit in the early weeks of Covid (2 & 3)
* An easy way to detect unequal error variances, outliers, and non-linearity is through a residuals vs. fitted plot
* As you can see in the residuals vs. fitted plot, weeks 2, 3, and 18 stand out while the rest of the points are randomly scattered above and below the 0 line
* This suggests that the relationship may not be linear, which is also shown in the normal Q-Q plot where the line deviates from the fitted line toward the right

> What does this mean?
* This shows that mental health varied widely and was worse in the early weeks of Covid
* Towards the later weeks, there did not seem to be any outliers in terms of variance
* On average, mental health increased slightly


